---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(magick)

```

```{css}
body {
  color: white;
  background-color: #733493;
  line-height: 2;
  font-family: 'Raleway', sans-serif;
}
p {
  font-weight: normal;
  font-family: 'Quicksand', sans-serif;
}


h1 {
  font-size: 24pt;
  font-style: normal;
  font-weight: bold;
  text-align: center;
}
h2 {
  font-size: 18pt;
  font-style: normal;
  background-color: #9d4edd;
  font-weight: bold;
  text-align: center;
}

```

## Patterns of Phone Use in Public Spaces

This data is being collected to capture brief observations of people’s phone use in public spaces. Its purpose is to gather information about the type of phone activity observed, the context in which it occurs, and the approximate duration of use. The information collected will contribute to Statistics 220, Project 2, which focuses on identifying patterns in everyday phone behavior across different environments.

# Observed Phone Use by Location and Activity

```{r}

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTRTaioXRkrCqyQKO49F7zdTbDvV1BsqhdRlngD3tI0sfc-JLx63qtKP5AgqJ3iKKgJ6LVKt4Z1mIeP/pub?gid=824138341&single=true&output=csv"

logged_data <- read.csv(csv_file)

latest_data <- logged_data %>%
  rename(phone_activity = 2,
         minutes = 3,
         observ_loc = 4,
         time_of_day = 5)
```

## Observations by Location

```{r, echo=FALSE}
latest_data %>%
  ggplot(aes(x = observ_loc)) +
  geom_bar(fill = "#681768") +
  labs(title = "What are the most common locations of phone usage?",
       subtitle = "Observations of phone usage by Location",
       x = "Location of phone usage",
       y = "Amount of observations")

```

## Types of Phone Activity Observed

```{r, echo=FALSE}
latest_data %>%
  ggplot(aes(x = phone_activity)) +
  geom_bar(fill = "#681768") +
  labs(title = "What are common phone activities?",
       subtitle = "Types of Phone Activity Observed",
       x = "Activity Type",
       y = "Amount of observations")
```

## Dynamic Comments

```{r, echo=FALSE}
paste("The shortest observed phone usage time was", min(latest_data$minutes), "minutes.")
```

```{r, echo=FALSE}
paste("The longest observed phone usage time was", max(latest_data$minutes), "minutes.")
```

```{r, echo=FALSE}
summary_img <- image_blank(width = 1200, height = 150, color = "#733493") %>%
  image_annotate(
    text = paste0( "Phone Use Summary\n",
      "Min: ", min(latest_data$minutes), " minutes   |   ",
      "Max: ", max(latest_data$minutes), " minutes"),
     color = "white",
     size = 30,
     gravity = "center",
     font = "Quicksand")

summary_img
```
